---
title: Time Series
author: Gillian McNally
date: '2017-10-05'
slug: time-series
categories:
  - ggplot2
  - R
  - Rstudio
tags:
  - data science
  - data visualization
---

Here is another cool data visualization example using a times series graph

Just like the last post we have to make sure we dowload all the proper pakages and put them into library.

```{r message=FALSE, warning=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```


In this post we will view Babe Ruth's homeruns over his career in baseball. 

```{r}
query<-"SELECT yearID,HR FROM Batting WHERE playerID='ruthba01'"
result<-sqldf(query)
```

Now the best part, the graph! Again, using ggplot2 we will graph the line and points of the information we just collected, to form a time series.

```{r}
ggplot()+
  geom_point(data=result,aes(x=yearID,y=HR),size=1/2)+
  geom_line(data=result,aes(x=yearID,y=HR))+
  ggtitle("Babe Ruth's Homeruns by Year")+
  xlab("Year")+
  ylab("Number of Homeruns")
```

Hope you liked this example stay tuned for more R tutorials!