---
title: Histograms
author: Gillian McNally
date: '2017-10-05'
slug: histograms
categories:
  - ggplot2
  - R
tags:
  - data visualization
  - sql
  - histogram
---

Welcome back we are going to try a Histogram example!

Alright, in this example we will look at the weights of MLB players through the Master table in the Lahman database.` Make sure you have the following applications ready to work with:

```{r message=FALSE, warning=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```


This request uses the Master table to gather its data.

```{r}
query<-"SELECT weight FROM Master"
result<-sqldf(query)
```

Let's try it out using our handy tool ggplot2!

```{r}
ggplot()+
  geom_histogram(data=result,aes(x=weight),color="blue",fill="white",bins=60)+
  ggtitle("Distribution of Baseball Player Bodyweight")+
  xlab("Weight of player")+
  ylab("Number of players")
```

We can manipulate the color and size of bins (or width) in the histogram to create the perfect look.

```{r}
ggplot()+
  geom_histogram(data=result,aes(x=weight),color="blue",fill="white",bins=10)+
  ggtitle("Distribution of Baseball Player Bodyweight")+
  xlab("Weight of player")+
  ylab("Number of players")
```

These examples help us to see drastic change when modifying our histograms.

```{r}
ggplot()+
  geom_histogram(data=result,aes(x=weight),color="blue",fill="white",bins=100)+
  ggtitle("Distribution of Baseball Player Bodyweight")+
  xlab("Weight of player")+
  ylab("Number of players")
```

I hope this helps you with future data visualization techniques!
