---
title: Scatterplot Fun
author: Gillian McNally
date: '2017-10-05'
slug: scatterplot-fun
categories:
  - R
  - ggplot2
tags:
  - scatterplot
  - data science
  - data visualization
---

Let's learn how to create our own scatter plot!


First, we need to install the following pakages and store them by putting them into library.

```{r message=FALSE, warning=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```

Let's try to find some information using the packages we just installed. We are going to try to find career homeruns and strikeouts from players who had more than 400 homeruns. 

```{r}
query<-"SELECT playerID,sum(HR),sum(SO)
FROM Batting 
GROUP BY playerID
HAVING sum(HR)>400"
sqldf(query)
```

Now that you have the information, save it as result so that we can make a scatter plot.
```{r}
query<-"SELECT playerID,sum(HR) AS CareerHR,sum(SO) AS CareerSO
FROM Batting
GROUP BY playerID
HAVING sum(HR)>400"
result<-sqldf(query)
```

Let's now use ggplot2 to help us make a nice graph with the data we just collected. Feel free to add your own titles to make it look nice.

```{r}
ggplot()+
geom_point(data=result,aes(x=CareerSO,y=CareerHR),size=3)+
ggtitle("Career Strikeouts and Homeruns - The Best")+
xlab("Career Strikeouts")+
ylab("Career Homeruns")
```
